taxadb: A High-Performance Local Taxonomic Database Interface

### 2020-06-22 paper/manuscript.Rmd
Add Data availability statement.

>>>>

# Data Availability
Code for the R package can be found on GitHub at <https://github.com/ropensci/taxadb>. The taxonomic database is also stored on Github at <https://github.com/boettiger-lab/taxadb-cache>. The original taxonomic data is stored by the individual provider and can be found through the included citations.
